Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added data for number of training examples (ICN)

>>>>

Compared to gravitational differentiation, there is a larger delta between the number of errors on the validation set depending on the number of initial training examples used. Those with 128 examples in $\varsigma$ make 85\% more errors on average. However, iterative cluster nucleation with 128 examples still makes 19\% fewer errors than gravitational differentiation with 256 examples in $\varsigma$.
